Figures

### 2019-06-17 figures/09_stream_buffer.Rmd
use ag instead of mixed ag + row crops

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct, 
         category = cut(diff, breaks = c(Inf, 3, -65, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag_pct, stream_cultivated_crops, 
                diff, category)

# llid 6201 as a low stream ag
# llid 7026 as a high stream ag
llids <- c("6201", "7026")

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
  geom_abline(aes(slope = 1, intercept = 3)) +
  geom_abline(aes(slope = 1, intercept = -65)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  xlim(c(40, 100)) + ylim(c(0, 100))
```

>>>>

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(stream_ag > 0) %>%
  mutate(diff = stream_ag - ag, 
         category = cut(diff, breaks = c(Inf, 28, -28, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag, stream_ag, 
                diff, category, iws_ha) %>%
  arrange(diff)

# first llid is a low stream ag lake
# second llids is a high stream ag lake
llids <- c("4532", "96236")

ggplot(data = dt) +
  geom_point(aes(x = ag, y = stream_ag, color = category)) +
  geom_abline(aes(slope = 1, intercept = 28)) +
  # geom_abline(aes(slope = 1, intercept = 0)) +
  geom_abline(aes(slope = 1, intercept = -28)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag, y = stream_ag, label = lagoslakeid), nudge_y = 2) + 
  theme_cowplot() +
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  ylim(c(1, 100)) # + xlim(c(40, 100))

# dplyr::filter(dt, lagoslakeid %in% llids)
```
